A formal approach but practical approach in train regulation

### 2025-06-19 paper/main.tex
Various small modifications & simplification

%% Regulator's Program
\newcommand{\evGuard}[2]{\ensuremath{\mathtt{ev}(\trainFmt{#1}, #2)}}
\newcommand{\ev}[3]{\evGuard{#1}{#2}: #3}
\newcommand{\incr}[1]{{\mbox{\ensuremath{\mathtt{incr}(\posFmt{#1})}}}\xspace}
\newcommand{\turn}[2]{{\mbox{\ensuremath{\mathtt{turn}(#1, #2)}}}\xspace}

@@

\begin{itemize}
	\item The routing program specifies how the regulator should react to events (i.e. when a train enters a block). A program is a sequence of rules, which are described below.
	\item The token list, denoted $T$, is a function  $T: \blocks \to \Nat$ associating a token level to each block. Those tokens are used to prevent multiple trains accessing the same block at the same time.
	\item The waiting set is a set $W \subseteq \blocks \times \Nat \times \trains$. A triple $\tuple{\bid{id}, n, \tid{id}} \in W$ means block $\bid{id}$ must be protected against train $\tid{id}$ entering as long as $T(\bid{id}) < n$.
\end{itemize}

Overall, the regulator is a tuple $R = \tuple{E, T, W}$. By convention, applying $\incr{pid}$ to the regulator is applying it to the token field: $R \cdot \incr{pid} = (E, T \cdot \incr{pid}, W)$. We use the same convention for the other atoms. \todo{move below}

@@

The syntax of regulator programs is given by the terminal stmt in Grammar~\ref{gr:regulator_program}.
The program of the regulator is a set of rules, guarded by events. A rule $\ev{\tid{id}}{n}{A}$ denotes that upon entering the $n$-th block of its route, train $\tid{id}$ will trigger actions $A$. There are four kinds of actions: 
\begin{description}
	\item[\incr{\bid{id}}:] this updates the token $\bid{id}$ in $T$:  $T \cdot \incr{\bid{id}}  \triangleq T[\bid{id} \leftarrow T(\bid{id})+1]$
	\item [att(pid, v):] ...\todo{}
	\item [\turn{\sid{id}}{s}:] this instructs the regulator to turn the switch $\sid{id}$ into the $s$ state: $\sigma\cdot\turn{\sid{id}}{s} = \sigma[\sid{id} \leftarrow s]$
	\item [auth:] ...\todo{}
\end{description}

@@

\begin{grammar}[Regulator's rules, with $tid \in \trains$, $n \in  \Nat$, $\posFmt{pid} \in \blocks$, $sid \in \turnouts$, $s\in \internalState$.][h][gr:regulator_program]
	\firstcasesubtil{stmt}{\evGuard{\tid{id}}{n} : \nonterm{A}^\star}{}
	\firstcase{A}{\incr{\bid{id}}}{}
	\otherform{att(\bid{id}, v)}{}
	\otherform{\turn{\sid{id}}{s}}{}
	\otherform{auth}{}
\end{grammar}

>>>>

%% Regulator's Program
\newcommand{\regTuple}[3]{\tuple{#1, #2, #3}}
\newcommand{\evGuard}[2]{\ensuremath{\mathtt{ev}(\trainFmt{#1}, #2)}}
\newcommand{\ev}[3]{\evGuard{#1}{#2}: #3}
\newcommand{\incr}[1]{{\mbox{\ensuremath{\mathtt{incr}(\posFmt{#1})}}}\xspace}
\newcommand{\turn}[2]{{\mbox{\ensuremath{\mathtt{turn}(#1, #2)}}}\xspace}
\newcommand{\tokens}{\ensuremath{T}}
\newcommand{\tokenOf}[1]{\ensuremath{T(\posFmt{#1})}}

@@

\begin{itemize}
	\item The routing program $E$ specifies how the regulator should react to events (i.e. when a train enters a block). A program is a sequence of rules, which are described below.
	\item The token list, denoted $\tokens$, is a function  $\tokens: \blocks \to \Nat$ associating a token level to each block. Those tokens are used to prevent multiple trains accessing the same block at the same time.
	\item The waiting set is a set $W \subseteq \blocks \times \Nat \times \trains$. A triple $\tuple{\bid{id}, n, \tid{id}} \in W$ means block $\bid{id}$ must be protected against train $\tid{id}$ entering as long as $\tokenOf{\bid{id}} < n$.
\end{itemize}

Overall, the regulator is a tuple $R = \regTuple{E}{\tokens}{W}$. By convention, applying $\incr{pid}$ to the regulator is applying it to the token field: $R \cdot \incr{pid} = (E, T \cdot \incr{pid}, W)$. We use the same convention for the other atoms. \todo{move below}

@@

The syntax of regulator programs is given by the non-terminal {\ttfamily stmt} in Grammar~\ref{gr:regulator_program}.
The program of the regulator is a set of rules, guarded by events. A rule $\ev{\tid{id}}{n}{A}$ denotes that upon entering the $n$-th block of its route, train $\tid{id}$ will trigger actions $A$. There are four kinds of actions: 
\begin{description}
	\item[\incr{\bid{id}}:] this updates the token $\bid{id}$ in $T$:  $T \cdot \incr{\bid{id}}  \triangleq T[\bid{id} \leftarrow T(\bid{id})+1]$
	\item [att(pid, v):] ...\todo{}
	\item [\turn{\sid{id}}{s}:] this instructs the regulator to turn the switch $\sid{id}$ into the $s$ state: $\sigma\cdot\turn{\sid{id}}{s} = \sigma[\sid{id} \leftarrow s]$
	\item [auth:] ...\todo{}
\end{description}

@@

\begin{grammar}[Regulator's rules, with $\tid{id} \in \trains$, $n \in  \Nat$, $\bid{id} \in \blocks$, $\sid{id} \in \turnouts$, $s\in \internalState$.][h][gr:regulator_program]
	\firstcasesubtil{\ttfamily stmt}{\evGuard{\tid{id}}{n} : \nonterm{A}^\star}{}
	\firstcase{A}{\incr{\bid{id}}}{}
	\otherform{att(\bid{id}, v)}{}
	\otherform{\turn{\sid{id}}{s}}{}
	\otherform{auth}{}
\end{grammar}
